Kindly Bent to Free Us

### 2018-11-07 kindly/infer/infer.tex
Blip.
A bit more structure.
Start working on the inference spec.

\documentclass[manuscript,author]{acmart}\settopmatter{printfolios=true}

% Encoding and lang
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

% Graphical packages
\usepackage{graphicx}

% Math
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
% \usepackage{mathrsfs}
\usepackage{mathtools}
% \usepackage{textcomp}
% \usepackage{textgreek}

\usepackage{caption}
\usepackage{subcaption}

\usepackage{natbib}% Good citations and bibliography
\usepackage{mathpartir} % Syntax trees
\usepackage[nameinlink,capitalize]{cleveref}

\bibliographystyle{ACM-Reference-Format}
\citestyle{acmauthoryear}

\input{prelude}
\input{notations}

\begin{document}

\title{Kindly Bent to Free Us}
\maketitle

\begin{figure*}[h]
  \centering
  \input{syntax}
  \caption{Syntax}
\end{figure*}
\begin{figure*}[h]
  \input{kinds}
  \caption{Constraint rules -- $\entail{C}{k}$ }
\end{figure*}
\begin{figure*}[h]
  \input{types}
  \caption{Type validity rules -- $\tyval{C}{\E}{\tau}$ }
  \input{inference}
  \caption{Inference rules -- $\inferW{\Sigma}{(C,\psi)}{\bf{\E}}{\bf{e}}{\tau}$ }
\end{figure*}
% \begin{figure*}[h]
%   \input{semantics}
%   \caption{Reduction rules -- $\ered{I}{E}{e}{v}$ }

% \end{figure*}

@@

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

>>>>

\section{Type inference}

We now formulate type inference for the \lang language. Our inference technique is based on the HM(X) framework~\citep{DBLP:journals/tapos/OderskySW99} which
presents how to merge Hindley-Milner type inference for let-polymorphism and
constraint solving. We first present our constraint language, we then show
our slight extension of HM(X) that support a kind system and affine types.

\subsection{Constraint language}

We consider $\mathcal C$ the set of constrains.
The grammar of constrains, presented
in \cref{grammar:constraint}, follows the traditional HM(X) formulation
with conjunctions,projections and type inequalities. The only new
element specific to our approach are kind equalities.
Entailment is noted $\entail{C}{D}$, where $D$ is a consequence of the
constraints $C$. The entailment rules are provided in \cref{rules:entail}.

\begin{figure}[h]
  \centering
  \begin{align*}
    C ::=&\ \Cleq{\tau_1}{\tau_2}\ |\ \Cleq{k_1}{k_2}\ |\ C_1 \Cand C_2\ |\ \Cproj{\alpha}{C}
  \end{align*}
  \caption{The constraint language}
  \label{grammar:constraint}
\end{figure}

\begin{figure*}[h]
  \input{infer/entails}
  \caption{Entailment rules -- $\entail{C}{D}$ }
  \label{rules:entail}
\end{figure*}

\paragraph{Solved forms}

The set of solved forms, noted $\mathcal S$,
is the set of constraints than can be used inside
type and kind schemes. $\mathcal S$ is composed only of kind
inequalities \emph{over variables}. For convenience, if $C\in\mathcal S$, we
note $C$ as a list of kind inequalities: $\Cleq{\kvar_i}{\kvar_{i'}}^n$.
\TODO{Extend the properties of solved forms}

We consider the existence of a function $\normalize$ which takes
a constraint in $\mathcal C$ and a unifier $\psi$ and returns a constraint
in solved form $C'$, and an updated unifier.

\subsection{Kind inference}

We note $\inferK{(\unif,C)}{\E}{\tau}{k}$ the fact that type $\tau$ has kind $k$
in environment $\E$ with constraints $C$ and unifier $\unif$. From an
algorithmic point of view, $\E$ and $\tau$ are the input parameters of
our inference procedure.

\subsection{Type inference}

\begin{figure*}[h]
  \input{infer/validity}
  \caption{Type validity rules -- $\tyval{C}{\E}{\tau}$ }
  \input{infer/rules}
  \caption{Inference rules -- $\inferW{\Sigma}{(C,\psi)}{\bf{\E}}{\bf{e}}{\tau}$ }
\end{figure*}

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../main"
%%% End:
